Direction-aware functional class scoring enrichment analysis of Infinium DNA methylation data

### 2023-12-21 manuscript/manuscript.Rmd
add gmts

---
title: "Finally, a functional class scoring method for enrichment analysis of Infinium DNA methylation data"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
bibliography: manuscript.bib
csl: epigenetics.csl
---

>>>>

---
title: "Direction-aware functional class scoring enrichment analysis of Infinium DNA methylation data"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
bibliography: manuscript.bib
csl: epigenetics.csl
---
